### 2020-10-13 Analysis/Code/Sorokin_JMP_2020.Rmd
Improved writing

 abstract: |
  \onehalfspacing \noindent 
  I document that firms in online marketplaces use price promotions 
  to facilitate transitions to better review tiers (similar to the number of stars on
  Amazon.com). I find that firms close to going one tier up are 4-9% more 
  likely to discount. I theorize that two effects could be at play. The selection effect 
  arises because customers who buy during a discount could be different from the regular 
  ones, and could potentially leave more positive reviews. The variance effect reflects 
  the idea that positive reviews could help the firm move up a review tier, while 
  negative reviews would keep the tier unchanged, minimizing the downside risk 
  of giving a discount. To test my hypotheses, I estimate a simple structural 
  model of demand and reviewing behavior, and develop a new approach to estimating demand 
  from data on product usage. I do not find evidence that the selection effect is 
  positive. I find evidence of the importance of the variance effect: when 
  the selection effect is zero, firms close to downgrading their review tier are 6% 
  less likely to give a discount, consistent with preferring less variance. I also 
  find that consumers are significantly more likely to leave a review when purchasing 
  during a discount. Additional findings include estimates of the causal effect of 
  reviews on sales and equilibrium discount elasticities in an important market 
  not previously studied. \thispagestyle{empty}

 bibliography: reviewsBib.bib
 fontsize: 12pt
 geometry: margin=1in
 link-citations: true
 linkcolor: mypink
 filecolor: myblue
 citecolor: mypink
 urlcolor: mypink
---

@@

In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17, p.379]. A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfactory without guidance. Such guidance is now routinly provided by different types of recommendation systems. Many marketplaces or third party websites allow consumers to review products and services that they purchased, and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives. These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*. Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services. Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews important, if not crucial, for the success of the business. Not surprisingly, firms assume an active approach to managing their reviews. Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.

In this paper I study a novel form of review management. I show that firms can use discounting in order to facilitate *transitions* between review tiers. Imagine a product that is several good reviews short of obtaining an additional star. I ask: would it be profitable for such a product to run a price promotion?  With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect. Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews. If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, as new customers are likely to leave positive reviews and help the product advance to the next review tier.  Whether the selection effect is positive or negative is an empirical question, and I answer this question with my data. The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier. Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews might not affect its review status---and, therefore, sales---by much. While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down. Fearing to lose that precious star, such products would prefer to delay running a price promotion, unless the selection effect is positive and strong.

To quantify all these effects, I analyze data from Steam, a major marketplace for computer video games. I build and estimate a simple structural model of demand and reviewing behavior on Steam. The demand part of the model lays the groundwork for my analysis. I confirm the importance of better review tiers for sales on Steam, finding a premium of as high as 10% of being in the best bin, and a penalty of up to 13% for not having reviews, compared to a mediocre review tier. My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 25% spike in sales. Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers on sales. I further document that these incentives translate into action. I find that products that are close to upgrading their review tier are 4-9% more likely to be on a discount, and I find some evidence that proximity to a downward transition decreases the probability to be on a discount by up to 4%.

My structural model provides further insight into the relative contributions of the variance and the selection effects to the observed behavior. I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products that are close to a review downgrade are 6% less likely to discount, which is consistent with the idea that the variance effect is negative for such products. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.

While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing that I contribute to. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. In a seminal contribution to this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random. Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), review scores of products on review platforms are moving slowly and are tested against the threshold on a daily basis. If a product is slightly below the cutoff and has 4 stars, why would it not try to do something to cross the cutoff, especially if better review bins are more lucrative? My paper asks precisely that question, and shows that such concerns are well-founded. I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers, but my findings could inform further inquiry into the subject.

@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on outcomes. To my knowledge, it was the first paper to use Steam as the object of its analysis. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data. I inherit the data from that paper, but confront the absence of sales data in a new way. I make assumptions about the gaming patterns for the games in my sample, and formulate a structural model of the data generating process. With the help of this model, I manage to extract information on product sales from usage data. I compare the estimates of the structural model with the ones obtained by its simpler regression analog, and find important similartities and dissimilarities. The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provide similar evidence for restaurants on Yelp. A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives. @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to. In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity. The idea is that consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether price promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service. In other words, @ByersEtAl12 documents a negative selection effect on Yelp. It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher. This difference can explain the reasons behind the dissatisfaction of the Groupon customers. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. There are a couple of other studies that dispute the negativity of the selection effect. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback. The effect is explained by clients reciprocating to the rebate, rather than byt the differences between customers buying with a rebate and without it. My study contributes to this debate by documenting the absence of a positive selection effect in a new market. Additionally, my paper is the first to focus on discrete changes in review tiers that follow the discounts, instead of studying the continuous effect of a discount on the review score.

Based on its findings, @ByersEtAl12 cautions businesses against running price promotions in an attempt to poach new customers and improve their online reputation. To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, this finding presents a puzzle. A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy. I provide a novel mechanism--- the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative. The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small. After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial. If this reasoning is commonplace, then the researcher would observe free pricing to deteriorate review scores, on average, but the average effect on sales would be positive.

The rest of this paper is organized as follows. Section \ref{dataSection} describes the institutional setting and the data I use. Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam. The technical nature of the material in this section contributes greatly to its size, but the goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers. The main findings are described in  Section \ref{descriptiveEvidence}. It opens with a stylized model of discounting for a product close to a review tier transition, and introduces the selection and the variance effects. The section proceeds by establishing that such discounting behavior takes place in the data. Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effects to the observed patterns of discounting around review transitions. Section \ref{conclusion} concludes.

@@

Any user who owns a game on Steam can leave a review for that game. Starting from late 2016 Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This gives me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors [@steamPurge]. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review tiers* to each game\footnote{I use words “tier”, “bin”, and “label” interchangebly througout the text}. These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each title, such as its name, price, and if the game is currently on a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an omage to the masterfuly chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on sales should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience. I used these update announcements to measure the number of updates each game had. Games with more than 5 small updates in the sample were excluded. Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}. Unobserved dynamic quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales. Consider a game that has just issued a major update. It is a great time for the firm to give a discount in order to rekindle the interest in the game. That update could also help the game transition to a better review tier, thanks to the positive reception of the new content. Thus, game updates could give rise to a correlation between discounting decisions and review transitions that is not causal. Given the fact that the update history is an imperfect way to monitor the update activity, I decided to be conservative and to eliminate as many potential updaters as I could. For that same reason I drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content. Finally, I drop games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.

@@

Before I start my investigation into the discounting behavior of the products close to a review transition, it is important to address two question. First, do discounts matter on Steam? Do they generate enough additional sales to be relevant? While the answer might be obvious for large sought-after products, the situation is less clear for an average game. The second question is: how big are the differences between different review tiers? If transitioning to a better tier does not increase sales by much, then firms would be unlikely to pursue such transitions when making on their discount decisions. The discussion of the assumptions behind my analysis and the interpretation of the parameter estimates contributes greatly to the size of this section. However, the main takeaways are simple: better review labels improve sales, and discounts are important drivers of sales on Steam. Having few reviews or having negative reviews depresses sales by 5-13% compared to having “Mixed” reviews; the “Overwhelmingly Positive” review tier increases sales by about 10% compared to “Mixed”. An average discount in the sample increases sales by 38% upon introduction, and by another 3-12% every day thereafter. These two facts form the foundation of my analysis of discounting behavior on a verge of a review tier transition that will be carried out in Section \ref{descriptiveEvidence}. I will further extend the model from this section by modelling the reviewing behavior of customers in Section \ref{selectionEffect}.

@@

Every buyer of game $i$ is a potential reviewer. I assume that a buyer who buys the game at $t-k$ leaves a positive (negative) review for the game on day $t$ with probability \(r_{it}^+\)	 (\(r_{it}^-\)), and no review otherwise. For the reasons I will explain later, I will refer to  $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.  The focus of the analysis is on the difference between the reviews left on and off a discount. To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm and other covariates as  as follows.

>>>>

 abstract: |
  \onehalfspacing \noindent 
  I document that firms in online marketplaces use price promotions to facilitate transitions to better review tiers (similar to the number of stars on Amazon.com). I find that firms close to going one tier up are 4-9% more likely to discount. I theorize that two effects could be at play. First, a selection effect arises because customers who buy during a discount could be different from the regular ones, and could potentially leave more positive reviews. Second, a variance effect reflects the idea that positive reviews could help the firm move up a review tier, while negative reviews would keep the tier unchanged, minimizing the downside risk of giving a discount. To test my hypotheses, I estimate a simple structural model of demand and reviewing behavior, and develop a new approach to estimating demand from data on product usage. I do not find evidence that the selection effect is positive. I find evidence of the importance of the variance effect: when the selection effect is controlled for, firms close to downgrading their review tier are 6% less likely to give a discount, consistent with preferring less variance. I also find that consumers are significantly more likely to leave reviews during a discount. Additional findings include estimates of the causal effect of reviews on sales and equilibrium discount elasticities in an important market not previously studied. \thispagestyle{empty}

 bibliography: reviewsBib.bib
 nocite: | 
  @stargazer, @texreg, @here, @dataframe, @plm
 fontsize: 12pt
 geometry: margin=1in
 link-citations: true
 linkcolor: mypink
 filecolor: myblue
 citecolor: mypink
 urlcolor: mypink
---

@@

In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17, p.379]. A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfyingly without guidance. Such guidance is now routinely provided by different types of recommendation systems. Many marketplaces or third party websites allow consumers to review products and services that they purchased, and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives. These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*. Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services. Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are important, if not crucial, for the success of the business. Not surprisingly, firms take an active approach to managing their reviews. Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors. In this paper I study a novel form of review management. I show that firms can use discounting in order to facilitate *transitions* between review tiers. Imagine a product that is several good reviews short of obtaining an additional star. I ask: would it be profitable for such a product to run a price promotion?

With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect. Customers who purchase the good during a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews. If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier. However, these new customers could also prove to be a worse match with the product and end up leaving less favorable reviews. Thus, the sign of the selection effect is ultimately an empirical question. The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier. Additional positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews might not affect its review status---and, therefore, sales---by much. While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down. Fearing to lose that precious star, such products would prefer to delay running a price promotion, unless the selection effect is positive and strong.

To quantify all these effects, I analyze data from Steam, a major marketplace for computer video games. I build and estimate a tractable structural model of demand and reviewing behavior on Steam. The demand model lays the groundwork for my analysis, as it helps me confirm the importance of better review tiers for sales on Steam. I find a premium of as high as 10% of being in the best bin and a penalty of up to 13% for not having reviews, compared to a mediocre review tier. My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 25% spike in sales. Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers to sales.

I further document that these incentives translate into action. I find that products that are close to upgrading their review tier are 4-9% more likely to sell at a discount, and I find some evidence that proximity to a downward transition decreases the probability to sell at a discount by up to 4%. I then employ my structural model to disentangle the relative contributions of the variance and the selection effects to the observed discounting patterns. To that end, I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level, and control for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products that are close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification that does not control for the selection effect. This finding is consistent with the idea that such products are averse to variance in their review scores. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.

While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing to which I contribute. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. In a seminal contribution to this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, which reaffirms the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploits the differences between two video games consoles rather than websites, and finds that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random. Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), review scores of products on review platforms are moving slowly and are tested against the threshold on a daily basis. If a product is slightly below the cutoff, why would it not try to do something to cross the cutoff, especially if better review bins are more lucrative? My paper asks precisely that question, and shows that such concerns are well-founded. I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers, but my findings could inform further inquiry into the subject.

@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on product outcomes. To my knowledge, it was the first paper to use Steam to study the causal effect of online reviews. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data. I inherit the data from that paper, but confront the absence of sales data in a new way. I make assumptions about the gaming patterns for the games in my sample, and formulate a structural model of the data generating process. With the help of this model, I manage to extract information on product sales from usage data. I compare the estimates of the structural model with the ones obtained by its simpler regression analog, and find important similartities and dissimilarities. The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provides similar evidence for restaurants on Yelp. A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives. @GuYe14 provides evidence that consumers who had left a negative review of their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to. In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity. The idea is that consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Anything that could affect the satisfaction of the customers could have an effect on their reviewing behavior, at least in principle. Another strand of literature is studying whether price promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service. In other words, @ByersEtAl12 documents a negative selection effect on Yelp. It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher. Worse match quality between the restaurants and the exploring Groupon customers could explain the dip in the review score following a price promotion. @Li16 confirms the finding in the same market, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. There are a couple of other studies that dispute the negativity of the selection effect. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback. The effect is explained by clients reciprocating to the rebate, rather than by the differences between customers buying with a rebate and without it. My study contributes to this debate by documenting the absence of a positive selection effect in a new market. Additionally, my paper is the first to focus on discrete changes in review tiers that follow the discounts, instead of studying the continuous effect of a discount on the review score.

Based on its findings, @ByersEtAl12 cautions businesses against running price promotions in an attempt to poach new customers and improve their online reputation. To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, this finding presents a puzzle. A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy. I provide a novel mechanism---the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative. The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small. After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial. If this reasoning is commonplace, then the researcher would observe free pricing to deteriorate review scores, on average, but the average effect on sales would be positive.

The rest of this paper is organized as follows. Section \ref{dataSection} describes the institutional setting and the data I use. Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam. The technical nature of the material in that section contributes greatly to its size, but the purpose of that section is to simply lay the groundwork for the main analysis by quantifying the importance of different review tiers on sales, and by showing that discounts are effective in attracting new customers. The main findings are described in  Section \ref{descriptiveEvidence}. It opens with a stylized model of a discounting decision for a product close to a review tier transition, and introduces the selection and the variance effects. The section proceeds by establishing that such discounting behavior takes place in the data. Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} with a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effects to the observed patterns of discounting around review transitions. Section \ref{conclusion} concludes.

@@

Any user who owns a game on Steam can leave a review for that game. Starting from late 2016 Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). Steam is, thus, different from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This gives me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors [@steamPurge]. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review tiers* to each game\footnote{I use the words “tier”, “bin”, and “label” interchangebly througout the text}. These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each title, such as its price or if the game is currently sold at a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an homage to the masterfully chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative” have a very similar contribution to visibility on the platform, which implies, among other things, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on sales should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience. I used these update announcements to measure the number of updates each game had. Games with more than 5 small updates in the sample were excluded. Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}. Unobserved dynamic quality would present a big obstacle to the identification of the effect of reviews on discounting decisions or sales. Consider a game that has just issued a major update. It is a great time for the firm to give a discount in order to rekindle the interest in the game. That update could also help the game transition to a better review tier, thanks to the positive reception of the new content. Thus, game updates could give rise to a correlation between discounting decisions and review transitions that is not causal. Given the fact that the update history is an imperfect way to monitor the update activity, I decided to be conservative and to eliminate as many potential updaters as I could. For that same reason I drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content. Finally, I drop games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.

@@

Before I start my investigation into the discounting behavior of the products close to a review transition, it is important to address two question. First, do discounts matter on Steam? Do they generate enough additional sales to be relevant? While the answer might be obvious for large sought-after products, the situation is less clear for an average game. The second question is: how big are the differences between various review tiers? If transitioning to a better tier does not increase sales by much, then firms would be unlikely to pursue such transitions when making their discount decisions. The discussion of the assumptions behind my analysis and the interpretation of the parameter estimates contributes greatly to the size of this section. However, the main takeaways are simple: better review labels improve sales, and discounts are important drivers of sales on Steam. Having few reviews or having negative reviews depresses sales by 5-13% compared to having “Mixed” reviews; the “Overwhelmingly Positive” review tier increases sales by about 10% compared to “Mixed”. An average discount in the sample increases sales by 38% upon introduction, and by another 3-12% every day thereafter. These two facts form the foundation of my analysis of discounting behavior on a verge of a review tier transition that will be carried out in Section \ref{descriptiveEvidence}. I will further extend the model from this section by modelling the reviewing behavior of customers in Section \ref{selectionEffect}.

@@

Every buyer of game $i$ is a potential reviewer. I assume that a buyer who buys the game at $t-k$ leaves a positive (negative) review for the game on day $t$ with probability \(r_{it}^+\)	 (\(r_{it}^-\)), and no review otherwise. For the reasons I explain later, I will refer to $r_{it}^+$ as the *like rate*, and to $r_{it}^-$ as the *dislike rate*.  The focus of the analysis is on the difference between the reviews left on and off a discount. To that end, I parametrize the like and dislike rates to depend on the discounting behavior of the firm and other covariates as  as follows.
